\section{Details of \method Jailbreak Experiments}

\subsection{\method Components}
\label{assec:wildteaming_components}

\paragraph{Attack Model}

For a fair comparison with the \pair baseline, we adopt the same base attacker model, \mixtral, in the \method experiments (see detailed prompt in Table \ref{tab:compose_tactics_prompt}). To generate adversarial attacks, \method randomly samples several jailbreak tactics from tactics mined from in-the-wild user queries. For the jailbreak experiments in the main paper, we fix the tactic ``seed leading sentence,'' which seeds the model response by a leading sentence or a half-sentence to induce the model to comply with the harmful request. We make this choice to be consistent with and to remain competitive against \pair, as ``seed leading sentence'' is the repeatedly used jailbreak tactic by \pair. However, to improve the diversity of attacks, \method samples another three jailbreak tactics from \tacticbank to form the final attacks. We also show ablation results for \textit{not} fixing the ``seed leading sentence'' tactic in Table \ref{tab:jailbreak_results_full}. Although it has a slightly lower performance, it still outperforms \pair by a large margin. Finally, please refer to Table \ref{tab:jailbreak_results_full} for ablation results of forming attacks with different numbers of tactics. For all the experiments, we generate attacks with a max length of 1024 tokens, with a temperature of 1 and a top-p of 0.9.

\input{tables/compose_jailbreak_tactics_prompt}
\input{tables/example_attacks_from_diff_jailbreak_methods}
\input{tables/example_attacks_2}
\input{tables/example_attacks_3}
\input{tables/example_wt_attacks}

\paragraph{Target Model}
We evaluate the attacks generated by \method against several target models, including both \textit{open-source} models, \ie vicuna-7B \citep{vicuna2023}, \tulu-7B \citep{ivison2023tulu}, \mistral-7B \citep{jiang2023mistral}, \mixtral \citep{jiang2024mixtral}, and \textit{closed-source} models, \ie \chatgpt and \gptfour \citep{openai2024gpt4}. For evaluation consistency, we generate model completions of 512 tokens, with a temperature of 0 and top-p of 1 for all models and methods. Table \ref{tab:chat_model_format} shows the chat format and system messages used by the target models, consistent with the setup from \harmbench.
\input{tables/chat_model_format}

\paragraph{Low Risk Pruner}
During the jailbreak revision, the revised adversarial prompt may overly conceal the harmful intent of the original vanilla prompt, and thus present lower risk than originally, and thus may not elicit the target harmful response adhering to the original vanilla prompt. To effectively remove these lower-risk attacks, we use an in-house prompt harmfulness classifier that was trained to classify the harmfulness of a user prompt (see training details of the harmful prompt classifier in Appendix \ref{subsec:classifier_details}) to prune lower-risk candidate attacks that do not post strong enough threat to the language models' safety.

\paragraph{Off-topic Pruner}
During the jailbreak revision, the revised prompt may lose its original meaning and thus convey a different harmful intent than the original vanilla prompt. We thus reduce the number of unnecessary attack trials with off-topic pruning. To do so, we use a Natural Language Inference (NLI) classifier model \citep{liu2022wanli} to examine whether the revised adversarial jailbreak attack contradicts the original attack. NLI is a language task that determines if a ``hypothesis'' statement is true (entailment), false (contradiction), or undetermined (neutral) given a ``premise'' statement. To identify off-topics adversarial prompts, we examine if the adversarial revision still entails or remains neutral to the original vanilla prompt with a probability threshold of 0.9 for combining entailment and neutral.

\paragraph{Attack Selector}

\harmbench standardizes the evaluation of different jailbreaking methods into three stages for each given harmful vanilla behavior: (1) run the jailbreak method to select an attack candidate; (2) generate target model completion for the selected attack; (3) evaluate if the model completion presents the harmful content demand by the given vanilla harmful behavior. During step (1), different attack methods use different criteria for selecting the final attack, \eg loss (\gcg, \autodan), an intermediate validation classifier (\pair and \method). The choice of the intermediate validation classifier can largely influence the final attack success rate, as low precision attack selector may miss a quality attack candidate even if the jailbreak method successfully generates it. In the original \harmbench paper, the reported performance of \pair is significantly lower than that in our experiments (and that in the original \pair paper) because \harmbench opted to use a \mixtral-based selector, which has substantially lower precision than the GPT-4-based selector that the original \pair and we use.

Thus, for a more reliable selection of the final attack candidate, we use the combined signal of two attack selector models (a GPT-4 based scorer using the setup from \pair and a validation classifier provided by \harmbench) for both \method and \pair experiments. After picking the final attack candidate, we pass it to the \harmbench test classifier for the final ASR evaluation to attain comparable standard evaluation metrics to those reported in \harmbench.

For the diversity evaluations, we skip the step of using the attack selector to pick a candidate for the final test evaluation and directly use the final test classifier to evaluate the presence of a unique, successful attack among $c$ attack candidates. This is because the primary purpose of the diversity evaluation is to see if a method can find multiple unique successful attacks with $c$ attempts instead of evaluating if \textit{an} attack is successful or not as selected by an end-to-end jailbreak pipeline.

\subsection{\harmbench Benchmark}

We use the \harmbench benchmark \citep{mazeika2024harmbench} evaluation setup to compare \method to other jailbreak methods. \harmbench was introduced to standardize the evaluation of jailbreaking methods to evaluate \method. It contains four types of evaluation testing scenarios: 200 standard behaviors (straightforward unsafe requests across wide risk categories), 100 contextual behaviors (that consist of a behavior string with a contextualization string), 100 copyright behaviors (to test if a model generates copyrighted content), and 110 multimodal behaviors (consist of an image coupled with a behavior string). In our main jailbreak experiments, we report the final performance of methods using the test set's 159 standard behaviors (vanilla harmful prompts) because these are representative harmful cases that language models should account for. We use the 41 standard behaviors in the validation set to identify the best configuration of the method, and for the ablation experiments (see Table \ref{tab:jailbreak_ablations} and \ref{tab:jailbreak_ablations_full}).

\subsection{Jailbreak Method Baselines}

In our jailbreak experiments, we compare three state-of-the-art jailbreak methods with open-source code\footnote{\url{https://github.com/centerforaisafety/HarmBench}} as ranked by \harmbench. Note that we exclude TAP \citep{tap} due to computing constraints, as although it's a strong baseline, it presents a very similar extension of PAIR according to previous works.

\paragraph{\pair}~\citep{pair} uses an iterative prompting strategy to jailbreak the target LLM (either white-box or black-box model). Specifically, given a particular harmful behavior, the attacker LLM aims to generate an adversarial prompt that can elicit an on-target response for that behavior from the target LLM. The generated prompt is passed to the target model to produce the completions. PAIR then uses another judge LLM to judge whether the completion successfully elicits the target's harmful behavior. Based on the judgment, the attacker LLM iteratively revises its prompts until it finds a successful attack or hits the max iteration limit.

\paragraph{\autodan}~\citep{liu2023autodan} is an optimization-based method that uses a genetic algorithm to mutate a seed human-written attacking prompt to increase the log probability of the targeted adversarial suffix. As \autodan requires calculating the log probability of the text, it does not apply to black-box models.

\paragraph{\gcg}~\citep{gcg} is another optimization-based strategy that uses the gradient to maximize the log probability of the targeted adversarial suffix. Similar to \autodan, it cannot be applied to black-box models. \gcg method tends to produce gibberish texts that are not semantically meaningful.

\subsection{\method Full Results and Ablations}
\label{assec:jailbreak_ablations}

Table \ref{tab:jailbreak_ablations_full} shows the ablation results of the number and types of jailbreak tactics to compose and the effect of using or not using off-topic and low-risk pruning with the 41 validation standard vanilla prompts from \harmbench. This is an expanded version of Table \ref{tab:jailbreak_ablations} in the main paper. Results show that the best performances gain over \pair comes with composing 4 sampled jailbreak tactics while fixing one of them to be ``seed leading sentence,'' which is the predominant tactic used by \pair. Additionally, both low-risk and off-topic improves the performance compared to not using them, and the best performance gain comes from combining both pruning strategies.

Finally, we show example attacks from different attack methods in Table \ref{tab:example_attacks_from_dif_methods}, \ref{tab:example_attacks_from_dif_methods_2}, \ref{tab:example_attacks_from_dif_methods_3}, and further examples of \method attacks in \Cref{tab:example_wt_tactics}, \ref{tab:example_wt_tactics_2}, \ref{tab:example_wt_tactics_3}. 

\input{tables/jailbreak_ablations}

