
\section{Adversarial Training for Robust Refusal}\label{sec:adv_training}
An important use case for red teaming is hardening defenses against adversaries before deployment. While several system-level defenses have been proposed for LLMs, very few model-level defenses have been explored beyond standard fine-tuning and preference optimization on safety datasets \citep{ganguli2022red, achiam2023gpt, touvron2023llama}.

To explore the potential for codevelopment of automated red teaming methods and model-level defenses, we propose a new adversarial training method for robust refusal, called Robust Refusal Dynamic Defense (R2D2). As opposed to fine-tuning on a static dataset of harmful prompts, our method fine-tunes LLMs on a dynamic pool of test cases continually updated by a strong optimization-based red teaming method.



\subsection{Efficient GCG Adversarial Training}
We use GCG for our adversary, since we find that it is the most effective attack on robust LLMs like Llama 2. Unfortunately, GCG is extremely slow, requiring $20$ minutes to generate a single test case on 7B parameter LLMs using an A100. To address this issue, we draw on the fast adversarial training literature \citep{shafahi2019adversarial} and use persistent test cases.


\paragraph{Preliminaries.}
Given an initial test case $x^{(0)}$ and target string $t$, GCG optimizes the test case to maximize the probability assigned by an LLM to the target string. Formally, let $f_\theta(t \mid x)$ be the conditional PMF defined by the LLM $f$ with parameters $\theta$, where $t$ is a target string and $x$ is a prompt. Without loss of generality, we assume that there is no chat template for $f$. The GCG loss is $\mathcal{L}_\text{GCG} = -1 \cdot \log f_\theta(t \mid x^{(i)})$, and the GCG algorithm uses a combination of greedy and gradient-based search techniques to propose $x^{(i+1)}$ to minimize the loss \citep{zou2023universal}.

\paragraph{Persistent test cases.}
Rather than optimizing GCG from scratch in each batch, we use continual optimization on a fixed pool of test cases $\{(x_1, t_1), (x_2, t_2), \dotsc, (x_N, t_N)\}$ that persist across batches. Each test case in the pool consists of the test case string $x_i$ and a corresponding target string $t_i$. In each batch, we randomly sample $n$ test cases from the pool, update the test cases on the current model using GCG for $m$ steps, and then compute the model losses.

\begin{figure}
\begin{algorithm}[H]
\caption{Robust Refusal Dynamic Defense}
\label{algorithm:R2D2}
\begin{algorithmic}
\STATE {\bfseries Input:} ${(x_i^{(0)}, t_i) \mid 1 \leq i \leq N}$, $\theta^{(0)}$, $M$, $m$, $n$, $K$, $L$
\STATE {\bfseries Output:} Updated model parameters $\theta$
\STATE Initialize test case pool $P = {(x_i, t_i) \mid 1 \leq i \leq N}$
\STATE Initialize model parameters $\theta \leftarrow \theta^{(0)}$
\FOR{$iteration = 1$ {\bfseries to} $M$}
\STATE Sample $n$ test cases ${(x_j, t_j)}$ from $P$
\FOR{$step = 1$ {\bfseries to} $m$}
\FOR{each $(x_j, t_j)$ in sampled test cases}
\STATE Update $x_j$ using GCG to minimize $\mathcal{L}_\text{GCG}$
\ENDFOR
\ENDFOR
\STATE Compute $\mathcal{L}_\text{away}$ and $\mathcal{L}_\text{toward}$ for updated test cases
\STATE Compute $\mathcal{L}_\text{SFT}$ on instruction-tuning dataset
\STATE Update $\theta$ by minimizing combined loss\\\qquad\qquad$\mathcal{L}_\text{total} = \mathcal{L}_\text{away} + \mathcal{L}_\text{toward} + \mathcal{L}_\text{SFT}$
\IF{$iteration \mod L = 0$}
\STATE Reset $K\%$ of test cases in $P$
\ENDIF
\ENDFOR
\STATE {\bfseries return} $\theta$
\end{algorithmic}
\end{algorithm}
\end{figure}

\paragraph{Model Losses.}
Our adversarial training method combines two losses: an ``away loss'' $\mathcal{L}_\text{away}$ and a ``toward loss'' $\mathcal{L}_\text{toward}$. The away loss directly opposes the GCG loss for test cases sampled in a batch, and the toward loss trains the model to output a fixed refusal string $t_\text{refusal}$ instead of the target string for test cases sampled in a batch. Formally, we define
\begin{align*}
    &\mathcal{L}_\text{away} = -1 \cdot \log \left( 1 - f_\theta(t_i \mid x_i) \right) \\
    &\mathcal{L}_\text{toward} = -1 \cdot \log f_\theta(t_\text{refusal} \mid x_i)
\end{align*}

\paragraph{Full method.}
To increase the diversity of test cases generated by GCG, we randomly reset $K\%$ of the test cases in the pool every $L$ model updates. To preserve model utility, we include a standard supervised fine-tuning loss $\mathcal{L}_\text{SFT}$ on an instruction-tuning dataset. Our full method is shown in \Cref{algorithm:R2D2}.

