\begin{abstract}

We introduce \method, an automatic red-teaming framework that mines \textit{in-the-wild} user-chatbot interactions to discover 5.7K unique clusters of novel jailbreak tactics, and then composes selections of multiple mined tactics for systematic exploration of novel and even more challenging jailbreaks.
Compared to prior work that performed red-teaming via recruited human workers, gradient-based optimization, or iterative revision with large language models (LLMs), our work investigates jailbreaks from chatbot users in-the-wild who were not specifically instructed to break the system. \method reveals previously unidentified vulnerabilities of frontier LLMs, resulting in up to 4.6x more \emph{diverse} and \emph{successful} adversarial attacks compared to state-of-the-art jailbreaking methods.
% within a fixed amount of attack attempts. 

While there exist many datasets for jailbreak \emph{evaluation}, very few open-source datasets exist for jailbreak \emph{training}, as safety training data has been closed among all frontier models even when their weights are open. Therefore, with \method we create \dataset, a large-scale open-source synthetic safety dataset with 262K \textit{vanilla} (direct request) and \textit{adversarial} (complex jailbreak) prompt-response pairs. In order to mitigate exaggerated safety behaviors, 
\dataset provides two contrastive types of queries: 1) \textit{harmful} queries 
(both vanilla and adversarial) and 
2) \textit{benign} queries that resemble harmful queries in form but contain no harmful intent. As \dataset considerably upgrades the quality and scale of existing safety resources, it uniquely enables us to examine the \textit{scaling effects of data} and the \textit{interplay of data properties and model capabilities} during safety training. Through extensive model training and evaluations, we identify the training properties that enable an ideal balance of safety behaviors: appropriate safeguarding without over-refusal, effective handling of both vanilla and adversarial queries, and minimal, if any, decrease in general capabilities. All the components of \dataset contribute to achieving balanced safety behaviors of models.

\end{abstract}
