\section{Transport Audit and Refuse-Level Gate}
\label{app:audit}

The audit is an estimand-specific admissibility check. It does not ask whether
the policy is good. It asks whether the calibrated level estimate can be
interpreted as a level claim for this policy and tail level.

\subsection{Two Audit Moments}
\label{app:audit-formal}

At a regular population optimizer $t_\alpha^\star$, define
\begin{align}
g_1(O_\ptarget;t_\alpha^\star)
&=\one\{\Y\le t_\alpha^\star\}-\alpha,\\
g_2(O_\ptarget;t_\alpha^\star)
&=\shortfall{t_\alpha^\star}{\Y}
-h_{t_\alpha^\star}(\Sscore,\X).
\end{align}
The first moment checks whether the selected threshold captures the intended
tail mass. The second checks whether the calibrated shortfall transports at
that threshold.

\begin{theorem}[Two-moment audit target]
\label{thm:formal-two-moment}
Under \cref{ass:regular-tail,ass:shortfall-transport},
\[
\E_\ptarget[g_1(O_\ptarget;t_\alpha^\star)]=0,
\qquad
\E_\ptarget[g_2(O_\ptarget;t_\alpha^\star)]=0.
\]
\end{theorem}

\begin{twocolproof}
\twocolrow{
\[
t_\alpha^\star=q_\alpha(\ptarget),
\qquad
\Pp_\ptarget(\Y\le t_\alpha^\star)=\alpha.
\]
}{
\cref{ass:regular-tail} gives the regular quantile optimizer.
}
\twocolrow{
\[
\E_\ptarget[g_1(O_\ptarget;t_\alpha^\star)]
=\Pp_\ptarget(\Y\le t_\alpha^\star)-\alpha=0.
\]
}{
Take expectation of the tail-mass moment.
}
\twocolrow{
\[
\E_\ptarget[g_2(O_\ptarget;t_\alpha^\star)]
=\E_\ptarget[
\shortfall{t_\alpha^\star}{\Y}
-h_{t_\alpha^\star}(\Sscore,\X)].
\]
}{
This is the shortfall residual at the selected threshold.
}
\twocolrow{
\[
\E_\ptarget[g_2(O_\ptarget;t_\alpha^\star)]=0.
\]
}{
Apply \cref{ass:shortfall-transport} at $t_\alpha^\star$.
}
\end{twocolproof}

On an audit sample, use the fitted threshold and calibrator:
\begin{align}
\hat g_{1i}
&=\one\{\Y_i\le\hat t_\alpha\}-\alpha,\\
\hat g_{2i}
&=\shortfall{\hat t_\alpha}{\Y_i}
-\hat h_{\hat t_\alpha}(\Sscore_i,\X_i),
\end{align}
and let $\bar g_n=n^{-1}\sum_i(\hat g_{1i},\hat g_{2i})^\top$.

\subsection{Wald Gate}

Let $\Omega$ be the asymptotic covariance of $\sqrt n\bar g_n$, including the
first-order effect of fitting $\hat h_t$ and selecting $\hat t_\alpha$. Let
$\hat\Omega$ be a consistent estimator. The Wald statistic is
\begin{equation}
W_n=n\bar g_n^\top\hat\Omega^{-1}\bar g_n.
\label{eq:formal-wald}
\end{equation}

\begin{theorem}[Wald limit]
\label{thm:formal-wald-limit}
Suppose the two audit moments have mean zero, \cref{ass:nuisance} holds, and
\[
\sqrt n\bar g_n
=\frac{1}{\sqrt n}\sum_{i=1}^n\phi(O_i)+o_p(1),
\qquad
\E[\phi(O_i)]=0,\qquad
\E[\phi(O_i)\phi(O_i)^\top]=\Omega,
\]
with $\Omega$ nonsingular and $\hat\Omega\overset{p}{\to}\Omega$. Then
\[
W_n\rightsquigarrow\chi^2_2.
\]
\end{theorem}

\begin{twocolproof}
\twocolrow{
\[
\sqrt n\bar g_n
=n^{-1/2}\sum_{i=1}^n\phi(O_i)+o_p(1).
\]
}{
Use the assumed first-order expansion.
}
\twocolrow{
\[
\sqrt n\bar g_n\rightsquigarrow N(0,\Omega).
\]
}{
Apply the multivariate central limit theorem.
}
\twocolrow{
\[
\hat\Omega^{-1}\overset{p}{\to}\Omega^{-1}.
\]
}{
Use covariance consistency and nonsingularity.
}
\twocolrow{
\[
n\bar g_n^\top\hat\Omega^{-1}\bar g_n
\rightsquigarrow Z^\top\Omega^{-1}Z,\qquad Z\sim N(0,\Omega).
\]
}{
Apply Slutsky's theorem and the continuous mapping theorem.
}
\twocolrow{
\[
Z^\top\Omega^{-1}Z\sim\chi^2_2.
\]
}{
Whiten $Z$.
}
\end{twocolproof}

At audit level $\eta$,
\[
W_n>\chi^2_{2,1-\eta}
\quad\Longrightarrow\quad
\RefuseLevel.
\]
Rejected rows may be shown as diagnostics, but not interpreted as calibrated
level claims.

\subsection{Held-Out Audit Design}
\label{app:audit-holdout}

The audit slice must be disjoint from the rows used to train the calibrator.
When the target policy is the logger, the selected logger oracle rows are split
into a calibration portion and a held-out audit portion. When the target policy
differs from the logger, the target's selected oracle rows are already outside
the logger calibration sample, so they can serve as the target audit slice.

This split is not cosmetic. If the isotonic calibrator is audited on the same
rows it fit, residuals are mechanically shrunk and the audit no longer tests
transport.

\subsection{Interpreting Failures}
\label{app:audit-cells}

The two moments diagnose different failures:
\begin{itemize}[leftmargin=*,nosep]
\item small $|\bar g_1|$ and small $|\bar g_2|$: threshold and shortfall
transport both look credible; report the level estimate.
\item large $|\bar g_1|$ and small $|\bar g_2|$: the threshold is in the wrong
tail percentile, but conditional shortfall predictions are locally reasonable.
\item small $|\bar g_1|$ and large $|\bar g_2|$: the threshold captures the
right amount of mass, but the cheap-to-oracle shortfall map does not transport.
\item both large: refuse; both the tail boundary and the shortfall surface are
misaligned.
\end{itemize}

\subsection{Mean and CVaR Gates Are Not Nested}

Mean-CJE audits $\E_\ptarget[\Y-f(\Sscore,\X)]=0$. CVaR-CJE audits tail mass
and shortfall transport at $\hat t_\alpha$. Either gate can pass while the
other fails. A valid mean claim does not certify a tail claim, and a valid tail
claim does not certify a mean claim. Each reported estimand must be gated by
its own audit.
