\section{Full-Pipeline Bootstrap and Variance Taxonomy}
\label{app:bootstrap}

This appendix separates two questions that are easy to conflate:
\emph{where would the estimate move under a different oracle slice?} and
\emph{does the calibrator transport on the held-out audit slice?} The first is
estimator uncertainty. The second is audit uncertainty.

\subsection{Bootstrap Algorithm}

\begin{algorithm}[h]
\caption{Full-pipeline cluster bootstrap for Direct CVaR-CJE}
\label{alg:bootstrap}
\begin{algorithmic}[1]
\REQUIRE Logger oracle slice $\mathcal{O}$; target-policy cheap-score rows
$\{(\X_i,\Sscore_i)\}_{i=1}^{n_\ptarget}$; target audit slice
$\mathcal{A}_\ptarget$; threshold grid $\mathcal{T}$; tail level $\alpha$;
replicate count $B$; prompt-cluster map $c(\cdot)$.
\STATE Fit point-estimate shortfall calibrators $\hat h_t^{(0)}$ on
$\mathcal{O}$.
\STATE Select
$\hat t_\alpha^{(0)}\in\arg\max_{t\in\mathcal{T}}
\left[t-\alpha^{-1}n_\ptarget^{-1}\sum_i
\hat h_t^{(0)}(\Sscore_i,\X_i)\right]$.
\STATE Compute point estimate $\hat V_\alpha^{(0)}$ and audit moments
$(\bar g_1^{(0)},\bar g_2^{(0)})$.
\FOR{$b=1$ to $B$}
\STATE Resample prompt clusters with replacement.
\STATE Build replicate calibration rows, target evaluation rows, and audit rows.
\STATE Refit the shortfall calibrators $\hat h_t^{(b)}$ on the replicate
calibration rows.
\STATE Re-optimize
$\hat t_\alpha^{(b)}\in\arg\max_{t\in\mathcal{T}}
\left[t-\alpha^{-1}(n_\ptarget^{(b)})^{-1}
\sum_i\hat h_t^{(b)}(\Sscore_i^{(b)},\X_i^{(b)})\right]$.
\STATE Recompute $\hat V_\alpha^{(b)}$ and the audit moments at
$\hat t_\alpha^{(b)}$.
\ENDFOR
\STATE Use percentile quantiles of $\{\hat V_\alpha^{(b)}\}_{b=1}^B$ for the
estimate CI.
\STATE Use the covariance of bootstrap audit moments to estimate $\hat\Omega$
for the Wald gate in \cref{eq:formal-wald}.
\end{algorithmic}
\end{algorithm}

The cluster is the prompt. All policy rows tied to the same prompt move
together, preserving prompt-level dependence.

\subsection{Why Re-Optimize \texorpdfstring{$\hat t_\alpha$}{t-hat}}

The CVaR estimate is a supremum:
\[
\hat V_\alpha=\sup_{t\in\mathcal{T}}\hat\Psi_{\alpha,\ptarget}(t).
\]
The selected threshold can change when the calibration slice or evaluation
sample changes. Holding $\hat t_\alpha$ fixed inside bootstrap replicates
suppresses this argmax variation and gives intervals for the wrong functional.
Re-optimization is therefore part of the estimator, not a robustness extra.

\begin{remark}[The argmax wedge]
Mean-CJE has no threshold-selection nuisance. CVaR-CJE does. This is the main
reason its bootstrap and audit covariance need a full-pipeline treatment rather
than a fixed-threshold residual standard error alone.
\end{remark}

\subsection{Variance Taxonomy}
\label{app:variance-decomp}

There are two variance families:
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Estimator variance}: how much the level estimate moves under a
different calibration/evaluation draw. This is what bootstrap CIs on figures
should show.
\item \textbf{Audit variance}: how noisy the held-out residual moments are
when testing transport. This belongs in the gate, not as the figure's level CI.
\end{itemize}

For reporting a total uncertainty envelope, decompose
\begin{equation}
\Var_{\mathrm{total}}(\hat V_\alpha)
\approx
\Var_{\mathrm{cal}}(\hat V_\alpha)
+\Var_{\mathrm{audit}}(\hat V_\alpha).
\label{eq:var-total}
\end{equation}
Here $\Var_{\mathrm{cal}}$ is the variation from refitting the calibrator on a
different oracle slice. $\Var_{\mathrm{audit}}$ is the finite-sample variation
of the held-out audit residual average. Adding them is justified only when the
calibration and audit rows are disjoint, as in \cref{app:audit-holdout}.

\subsection{Mean-CJE and CVaR-CJE Inference Machines}

\begin{center}
\small
\begin{tabular}{p{0.22\linewidth}p{0.34\linewidth}p{0.34\linewidth}}
\toprule
 & Mean-CJE & CVaR-CJE \\
\midrule
Calibrator &
$\hat f(\Sscore,\X)\approx\E[\Y\mid\Sscore,\X]$ &
$\hat h_t(\Sscore,\X)\approx\E[(t-\Y)_+\mid\Sscore,\X]$ for each $t$ \\
Threshold &
none &
$\hat t_\alpha$ from a grid argmax \\
Audit moments &
one residual mean $\Y-\hat f(\Sscore,\X)$ &
tail mass $g_1$ and shortfall residual $g_2$ \\
Estimator bootstrap &
refit $\hat f$ &
refit $\hat h_t$ and re-optimize $\hat t_\alpha$ \\
Failure semantics &
average cheap-to-oracle residual does not transport &
tail mass, shortfall, or both do not transport \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Cost-Equivalence Definition}
\label{app:cost-equivalence}

For an audit-only baseline that computes empirical CVaR on the
$n_{\mathrm{audit}}$ oracle rows alone, define
\[
\sigma^2_{\mathrm{audit\_only}}=\mathrm{se}(\mathrm{audit\_only})^2,
\qquad
\sigma^2_{\mathrm{direct}}=\Var_{\mathrm{cal}}+\Var_{\mathrm{audit}}.
\]
The oracle-equivalent sample size is
\begin{equation}
\mathrm{cost\_ratio}
=\frac{\sigma^2_{\mathrm{audit\_only}}}{\sigma^2_{\mathrm{direct}}},
\qquad
n_{\mathrm{equiv}}
=\lceil n_{\mathrm{audit}}\cdot \mathrm{cost\_ratio}\rceil.
\label{eq:cost-equiv}
\end{equation}
This is a methodological diagnostic. Numerical ratios should be regenerated
for the current run and reported with the per-policy spread.
