\section{Arena-Tail Benchmark}
\label{sec:arena-tail}

The original Arena-style CJE data are useful for debugging but too small and too mean-focused to be the only evidence for a tail-risk paper. Arena-Tail is the planned benchmark contribution: a controlled policy-comparison dataset with enough lower-tail mass to stress CVaR-CJE.

\paragraph{Design requirements.}
\begin{itemize}[leftmargin=*,nosep]
\item Continuous bounded oracle outcome $\Y\in[0,1]$, preferably a weighted rubric fraction.
\item Prompt strata that create realistic lower-tail mass: general chat, adversarial harmful, adversarial benign, safety-sensitive direct requests, and domain-consequence prompts.
\item Policies with similar means but different lower tails.
\item At least one policy that should fail the audit, so refusal behavior is empirically visible.
\item Metadata retained for post-audit diagnosis: source dataset, harm category, domain, prompt style, and rubric family.
\end{itemize}

\paragraph{Prompt sources.}
The pragmatic construction is a stratified mixture. General prompts can come from Arena and WildChat-style pools \citep{Zheng2023Judging,Chiang2024ChatbotArena,Zhao2024WildChat}. Tail strata can come from HealthBench-style medical conversations \citep{OpenAI2025HealthBench}, BeaverTails and PKU-SafeRLHF \citep{Ji2023BeaverTails,Ji2024PKUSafeRLHF}, and adversarial/refusal resources such as WildJailbreak, HarmBench, and StrongREJECT \citep{Jiang2024WildTeaming,Mazeika2024HarmBench,Souly2024StrongREJECT}.

\begin{table}[t]
\centering
\small
\begin{tabular}{lrl}
\toprule
Stratum & Share & Purpose \\
\midrule
General chat & 45-55\% & preserve comparability with Arena-style evaluation \\
Adversarial harmful & 15-20\% & create lower-tail safety failures \\
Adversarial benign & 10-15\% & detect over-refusal tails \\
Safety-sensitive direct & 10-15\% & cover explicit harm categories \\
Medical / legal / support & 10-15\% & connect tail risk to high-consequence workflows \\
\bottomrule
\end{tabular}
\caption{Arena-Tail prompt mixture. Exact shares should be pre-registered before policy generation.}
\label{tab:arena-tail-mixture}
\end{table}

\paragraph{Policy panel.}
The benchmark should include five policies: base, near-clone, premium/frontier, safety-tuned or over-refusal, and adversarial/jailbroken. The target empirical pattern is not that every policy differs in mean. The target pattern is that at least two policies have near-equal means and materially different lower-tail CVaR.

\paragraph{Labeling.}
Cheap judge scores are collected on all responses. Oracle labels are collected on a simple random or pre-specified tail-stratified slice, with the sampling design recorded. If tail-stratified labeling is used, estimator formulas must include the sampling correction. The audit slice must be held out from calibrator fitting.

