\section{Introduction}
\label{sec:intro}

LLM evaluation pipelines increasingly use a cheap LLM-as-judge to rank
candidate models, compare system prompts, and grade individual responses.
On pairwise comparisons of chatbot responses (MT-Bench), GPT-4 agrees
with human experts $85\%$ of the time \citep{Zheng2023Judging}. That
headline number is reassuring, but it hides a problem. LLM judges are
noisy, and their errors aren't random. They reliably prefer longer
answers, the response shown first, and answers from their own model
family. They also shy away from the extremes,
so a raw judge average can drift above or below the true accuracy
depending on where the truth lies
\citep{Lee2025LLMJudgeReporting,Chen2026EfficientLLMJudge}. Cheaper,
smaller judges have it worse. Under a length-padding attack on MT-Bench,
the strongest judge in the pool fell for the padded response only
$9\%$ of the time, while the cheaper judges fell for it $91\%$ of the
time. The practical cost shows up in three
places. Reported A/B or leaderboard improvements can reflect judge bias
rather than real model gains. Rankings
between two policies (a different model, prompt, or sampling
configuration) can flip entirely once the cheap judge is swapped for
an oracle label \citep{LandesbergNarayan2026CJE}. And
naive $95\%$ confidence intervals on uncalibrated judge scores captured
the true value in zero of $50$ seeds in one Chatbot Arena benchmark.

Once the cheap judge is calibrated, the standard report is still a
mean: the average calibrated score across the evaluation set.
However, for many deployments the mean is not the right summary. A
medical-assistant LLM that gives perfect advice $90\%$ of the time and
recommends really unsafe doses on the remaining $10\%$ has an
acceptable average but catastrophic tail risk. HealthBench, the
benchmark we use, makes this concrete: it reports a \emph{worst-at-k}
score alongside the mean. A frontier model that scores $60\%$ on
average drops by roughly a third on its worst trial out of $16$. The
reason is simple: in a safety-critical domain like health, one bad
model response can outweigh many good ones
\citep{OpenAI2025HealthBench}. The pattern goes beyond medicine.
Standard LLM safety evaluations are routinely orders of magnitude
smaller than deployment, and rare failures (jailbreaks,
dangerous-information disclosures, power-seeking actions) that do not
surface during evaluation or beta testing can still appear at scale
\citep{Jones2025RareLLMBehaviors}. The natural summary for the worst
$\alpha$ fraction of cases is Conditional Value at Risk (CVaR), or
expected shortfall. CVaR is the standard coherent risk measure in
finance and insurance
\citep{AcerbiTasche2002}, and is now also a
standard risk-sensitive criterion in machine learning, used in
risk-sensitive reinforcement learning for autonomous driving, clinical
treatment planning, and robotics \citep{Du2023IteratedCVaR}.
Tail-risk evaluation of LLM judges, however, is rare, and this paper
aims to fill that gap.

There are several ways to calibrate the mean. One treats the cheap judge as
a noisy classifier and corrects its bias from a small labeled set
\citep{Lee2025LLMJudgeReporting}. Another learns the judge's typical
error directly and subtracts it \citep{Chen2026EfficientLLMJudge}. We
follow Causal Judge Evaluation (CJE) \citep{LandesbergNarayan2026CJE}.
The recipe has four steps. First,
set aside a small oracle slice (typically $5$--$25\%$ of the responses
you evaluate) and fit a curve from cheap judge score to expected
oracle label. Second, average that curve's predictions over every
response to get a policy estimate. Third, for each target policy,
draw a fresh oracle sample and check whether the average gap between
oracle and prediction is zero; if not, refuse to report a calibrated
number for that policy rather than report one you cannot trust.
Fourth, when reporting a confidence interval, account for two sources
of noise: the usual sampling noise on the responses you evaluated,
plus the noise in the calibration curve itself, which is large when
the oracle slice is small. A bootstrap that refits the curve inside
every replicate captures both; ignoring the second source produces
intervals that drastically undercover, because at small oracle slices
the calibration noise can account for more than half the total
variance.

CJE handles the mean. But the tail of a mean-calibrated predictor is
generally not the conditional mean of the tail
\citep{Allen2024TailCalibration}, so we cannot reuse mean-CJE directly
for tail-risk evaluation. We extend the recipe to tails. The
contribution is \textbf{CVaR-CJE}, an audit-gated tail-risk estimator
with three pieces:

\begin{enumerate}[leftmargin=*,nosep]
\item A \textbf{stop-loss calibrator.} Mean-CJE fits one calibration
curve from cheap judge score to expected oracle label. The naive
extension to CVaR is to take the tail of those calibrated predictions.
This is not consistent: even at the population level (with the
calibration curve exactly equal to the conditional mean), the
estimator is biased. A conditional mean smooths variability: the
calibrated prediction is less variable than the outcome it calibrates,
so its tail is compressed toward the center, and CVaR picks up exactly
that lost variability. Our fix is to change the calibration target.
We fit a \emph{family} of curves, one per candidate threshold on a
small grid, where each curve predicts the \emph{shortfall} below its
threshold (how far below the threshold the oracle outcome falls, in
expectation). The expected shortfall conditional on the cheap score
is a genuinely different function at each threshold, so no single
curve can stand in for the family. We then average each curve's
predicted shortfall over the policy's responses and pick the
threshold that maximizes the standard CVaR objective
\citep{RockafellarUryasev2000}. The order matters: we calibrate
first, then optimize the threshold.

\item A \textbf{two-moment transport audit.} On a held-out slice of
oracle labels for the target policy (when the target equals the
logger, we $80/20$-split the oracle rows so the calibrator never sees
the audit data), we check two things at the chosen threshold: did we
find the right \emph{fraction} of bad responses, and are the
calibrator's predictions of \emph{how bad} they are accurate on the
audit slice? A standard joint test refuses to report the calibrated
CVaR for any policy where either check fails. Reading which check
failed tells us which knob to turn: a fraction-mismatch points at the
threshold, a prediction-mismatch points at the calibrator. The
variance for the test reuses the same bootstrap as the CI, so the
noise from refitting the calibrators and re-picking the threshold is
baked in automatically. At the boundary case where we ask for the
whole distribution (the worst $100\%$ of responses), the audit
collapses to the standard mean-CJE residual test, so the same
machinery handles both estimands.

\item \textbf{Confidence intervals via a full-pipeline bootstrap.} To
get a CI, we resample whole prompts with replacement many times and,
inside each resample, redo the entire pipeline: refit the family of
calibrators, re-pick the best threshold, and recompute CVaR. The
spread of those estimates is the CI. Two design choices matter. We
resample at the prompt level rather than the response level, because
responses to the same prompt across different policies are
correlated; resampling responses individually would shrink the CI
artificially. We also re-pick the threshold inside every replicate,
because the threshold itself is a noisy quantity. Fixing it at the
point-estimate value would ignore that source of variability and
produce intervals that are too narrow.
\end{enumerate}

\paragraph{Empirical results.}
We evaluate on HealthBench \citep{OpenAI2025HealthBench}, a
rubric-graded medical-assistant benchmark from OpenAI. Each prompt
comes with a list of expert-written rubric criteria, each carrying a
signed point value, and a response's oracle score is the sum of
points it earns from satisfied criteria, normalized by the total
positive-points weight. About $93\%$ of prompts have at least one
criterion that \emph{deducts} points, so the score directly reflects
safety-relevant failures rather than only correctness. We take the
first $500$ prompts from the open-source evaluation subset. The cheap
judge is gpt-4o-mini and the oracle (treated as ground truth in our
experiments) is gpt-4.1. We compare five policies on the same prompt
set: a \textsc{base} gpt-4o-mini policy with a standard
medical-assistant system prompt; a \textsc{clone} that uses the same
model and prompt with a different sampling seed and serves as a
statistical control; a \textsc{premium} variant that swaps the model
to gpt-4.1; a \textsc{parallel} variant that keeps gpt-4o-mini but
uses a shorter, terser clinical system prompt; and an
\textsc{unhelpful} variant whose system prompt is deliberately
off-topic, serving as an adversarial probe of the safety claim. We
label a uniform $25\%$ of the responses with the oracle judge,
leaving roughly $130$ oracle-labeled rows per non-base policy for
the audit. The headline tail level is the worst $10\%$ of responses;
we also stress-test at the worst $20\%$.

On the worst $10\%$ of responses, CVaR-CJE cuts the mean absolute
error against the full-oracle ground truth from $0.20$ (the CVaR of
the raw cheap-judge scores, no calibration) to $0.08$, a roughly
$60\%$ reduction, and beats this cheap-only baseline on every one of
the five policies. The audit passes for every policy at the worst
$10\%$, and correctly flags the one transport failure on the panel
when we tighten the test to the worst $20\%$: the \textsc{unhelpful}
policy, where the calibrator's chosen threshold is hit by $36\%$ of
responses rather than the intended $20\%$ (binomial $p$-value below
one in a thousand). At small budgets like this one, where pure-oracle
CVaR estimation on roughly $130$ labels is visibly noisy, the
calibrator buys roughly four-fold variance reduction over the
oracle-only baseline. The whole pipeline runs in under $30$ seconds
per policy on a laptop.
