\section{The Method: CVaR-CJE}
\label{sec:method}

For a prompt $\X$, target policy $\ptarget$ generates response
$\A_\ptarget$. A cheap LLM judge returns score
$\Sscore_\ptarget = s(\X, \A_\ptarget)$ on every $(\X, \A_\ptarget)$ pair
we sample from $\ptarget$. An oracle returns label $\Y_\ptarget = y(\X,
\A_\ptarget) \in [0, 1]$ on a small slice. The mean value of policy
$\ptarget$ is $V(\ptarget) = \E_\ptarget[\Y]$.

\subsection{Stop-loss representation of CVaR}
\label{sec:method-stoploss}

For $\alpha \in (0, 1]$, the lower $\alpha$-quantile is
$q_\alpha(\ptarget) = \inf\{t : \Pp_\ptarget(\Y \le t) \ge \alpha\}$ and
we target the lower-tail conditional expectation
\begin{equation}
\CVaR_\alpha(\ptarget) = \sup_{t \in \R}\left\{\,t - \frac{1}{\alpha}
\E_\ptarget[\shortfall{t}{\Y}]\,\right\},
\label{eq:stoploss-cvar}
\end{equation}
the Rockafellar--Uryasev representation
\citep{RockafellarUryasev2000,RockafellarUryasev2002}. For continuous $\Y$
the optimizer is $q_\alpha(\ptarget)$ and the supremum equals
$\E_\ptarget[\Y \mid \Y \le q_\alpha(\ptarget)]$. For discrete $\Y$ the
supremum is the atom-split shortfall (\cref{app:estimands}). Estimating
$\CVaR_\alpha(\ptarget)$ reduces to a family of mean shortfall
estimation problems indexed by $t$.

\subsection{Calibration}
\label{sec:method-calibration}

Instead of training the cheap judge to predict the mean of $\Y$, we
train it to predict the \emph{stop-loss} $(t-\Y)_+$, the shortfall below
threshold $t$. For each $t$ on a fixed grid $\mathcal{T}$, fit an
isotonic calibrator on the logger's oracle slice,
\begin{equation}
\hat h_t(\Sscore, \X) \;\approx\; \E_{\pzero}[\shortfall{t}{\Y} \mid
\Sscore, \X],
\end{equation}
and use it as a surrogate for the conditional shortfall under the
target policy. The calibrator is an isotonic transformation of every
cheap score, applied before the threshold is optimized. It also
differs across $t$ because $\E[(t-\Y)_+ \mid \Sscore]$ is a different
function of $\Sscore$ at every $t$. We are not just rescaling the cheap
scores or shifting one threshold.

On fresh target-policy responses with cheap judge scores
$(\X_i, \Sscore_i)_{i=1}^{n}$, evaluate the surrogate stop-loss
objective and search the threshold grid:
\begin{equation}
\hat\Psi_{\alpha,\ptarget}(t) = t - \frac{1}{\alpha n}\sum_{i=1}^{n}
\hat h_t(\Sscore_i, \X_i),
\qquad
\widehat{\CVaR}_{\alpha}^{\mathrm{direct}}(\ptarget) =
\max_{t \in \mathcal{T}}\hat\Psi_{\alpha,\ptarget}(t),
\qquad
\hat t_\alpha = \arg\max_{t \in \mathcal{T}}
\hat\Psi_{\alpha,\ptarget}(t).
\label{eq:direct-estimator}
\end{equation}
Under the shortfall-transport assumption $\E_\ptarget[\shortfall{t}{\Y}
- h_t(\Sscore, \X)] = 0$ for $t$ near the oracle optimizer,
$\widehat{\CVaR}_{\alpha}^{\mathrm{direct}}(\ptarget)$ targets
$\CVaR_\alpha(\ptarget)$ (\cref{thm:formal-cvar-identification}).

\subsection{Audits}
\label{sec:method-audits}

We do not assume shortfall transport silently. On a held-out
target-policy audit slice with $(\Sscore_i, \Y_i)$ pairs, evaluate two
moments at the selected threshold:
\begin{equation}
\bar g_1 = \frac{1}{n_{\mathrm{audit}}}\sum_i \big(\one\{\Y_i \le
\hat t_\alpha\} - \alpha\big),
\qquad
\bar g_2 = \frac{1}{n_{\mathrm{audit}}}\sum_i \big(\shortfall{\hat t_\alpha}
{\Y_i} - \hat h_{\hat t_\alpha}(\Sscore_i, \X_i)\big).
\label{eq:audit}
\end{equation}
$\bar g_1$ asks: \emph{did we find the right fraction of bad responses?}
The empirical lower-tail mass at $\hat t_\alpha$ should equal $\alpha$
when the threshold transports.
$\bar g_2$ asks: \emph{did we accurately predict how bad they are?} The
calibrator's predicted shortfall should equal the empirical shortfall on
average when the cheap-to-oracle map transports. The Wald statistic
$W_n = n_{\mathrm{audit}}\,\bar g^\top\hat\Omega^{-1}\bar g$ has a
$\chi^2_2$ limit (\cref{thm:formal-wald-limit}). At audit level $\eta$,
the gate is
\begin{equation}
W_n > \chi^2_{2,\,1-\eta} \;\;\Longrightarrow\;\;
\textsc{Refuse-Level}.
\label{eq:gate}
\end{equation}
A rejected policy may be reported as a diagnostic point estimate. It
must not be interpreted as a calibrated $\CVaR$ level claim.

\subsection{Inference: full-pipeline bootstrap}
\label{sec:method-inference}

Confidence intervals come from a full-pipeline cluster bootstrap that
resamples train, evaluation, and audit data jointly, refits the
shortfall calibrators, and \emph{re-optimizes} $\hat t_\alpha$ inside
every replicate. Re-optimization is required: the saddle-point
objective trades off tail-mass against shortfall, so a bootstrap that
fixes $\hat t_\alpha$ at its single point estimate suppresses a
first-order nuisance and undercovers. We report 95\% percentile CIs on
the plug-in centre. \Cref{app:bootstrap} gives the full algorithm and the variance
decomposition (\cref{eq:var-total})
$\Var_{\mathrm{total}} \approx \Var_{\mathrm{cal}} + \Var_{\mathrm{audit}}$
that separates calibrator-fit and audit-slice noise; the two are
approximately independent because the calibration and audit slices are
disjoint by construction (\cref{app:audit-holdout}).

\paragraph{The $\alpha = 1$ connection.}
For $\Y \in [0, 1]$ the optimizer in \cref{eq:stoploss-cvar} can be
taken as $t \ge 1$, $\CVaR_1(\ptarget) = V(\ptarget)$, the first audit
moment is identically zero, and the second is the negative of the
mean-CJE residual. Mean-CJE is the full-distribution special case and
CVaR-CJE is the lower-tail extension. The same code path returns both
(\cref{app:alpha-one}).
