\section{Related Work}
\label{sec:related}

\paragraph{Calibrated LLM-as-judge inference.}
CJE calibrates cheap judge scores to oracle labels and audits transport
across policies \citep{LandesbergNarayan2026CJE}. Recent LLM-as-judge
work emphasizes reporting bias correction and uncertainty rather than
raw judge scores \citep{Lee2025LLMJudgeReporting,Chen2026EfficientLLMJudge,
Li2025CalibraEval}. CVaR-CJE complements that line of work. It changes
the estimand from a mean to a lower-tail risk functional, adds a
threshold-and-shortfall audit for that functional, and recovers the
original mean audit at $\alpha = 1$.

\paragraph{LLM judges and benchmarks.}
MT-Bench and Chatbot Arena established scalable judge-based comparison
protocols \citep{Zheng2023Judging,Chiang2024ChatbotArena}. G-Eval and
Prometheus-style evaluators study model-based grading quality
\citep{Liu2023GEval,Kim2024Prometheus2}. RewardBench evaluates reward
models used for preference and alignment pipelines
\citep{Lambert2024RewardBench}. These works motivate scalable
evaluation but generally do not provide audit-gated lower-tail
inference.

\paragraph{Tail risk and conformal prediction.}
CVaR (also called expected shortfall) is the standard coherent risk
measure with the stop-loss optimization form used here
\citep{RockafellarUryasev2000,RockafellarUryasev2002,AcerbiTasche2002}.
Our contribution is the audit-gated surrogate estimation of CVaR for
LLM policy evaluation, not CVaR itself. A natural neighbor is conformal
prediction, the standard tool for individual-response LLM uncertainty
\citep{Angelopoulos2021Gentle}. Conformal prediction returns predictive
intervals for individual responses. CVaR-CJE returns a confidence
interval for a population-level functional, the expected outcome on
the worst $\alpha$-fraction of responses under a target policy. The
two answer different deployment-time questions.

\paragraph{Safety and high-stakes evaluation.}
HealthBench motivates worst-case reliability in medical interactions
and provides a rubric-based path to continuous outcomes
\citep{OpenAI2025HealthBench}. BeaverTails, PKU-SafeRLHF, WildJailbreak,
HarmBench, and StrongREJECT provide prompt and evaluation resources for
harmful requests, adversarial prompting, and refusal behavior
\citep{Ji2023BeaverTails,Ji2024PKUSafeRLHF,Jiang2024WildTeaming,
Mazeika2024HarmBench,Souly2024StrongREJECT}. The auditable-assumption
framing follows a broader statistical idea. Surrogate relationships
can fail under context shift, so high-stakes use should rely on
checkable diagnostics rather than untested transport assumptions
\citep{FlemingDeMets1996,Lipsitch2010,TchetgenTchetgen2024}.
