\section{Experimental Setup}
\label{sec:setup}

\paragraph{Data.}
HealthBench is a rubric-graded medical-assistant benchmark
\citep{OpenAI2025HealthBench}. We use the first $n_0 = 500$ prompts
from the \texttt{oss\_eval} subset. Each prompt carries a list of
rubric criteria with signed integer point values. The aggregate oracle
score is $\Y = \sum_c p_c \cdot \one\{c\text{ satisfied}\} /
\sum_{c:\,p_c>0} p_c$. The score can be negative when negative-points
criteria fire and positive credit is sparse. We do not clip $\Y$. About
$93\%$ of prompts have at least one negative-points criterion, and a
substantial fraction of rows score exactly zero. The boundary atom at
zero motivates the saddle-point form of $\CVaR$ (\cref{eq:stoploss-cvar})
and the atom-split truth definition (\cref{app:estimands}).

\paragraph{Policies.}
We compare five policies on the same prompts. \textsc{base} is
gpt-4o-mini with a standard medical-assistant system prompt at sampling
seed 42. \textsc{clone} is identical to \textsc{base} except for the
sampling seed (43). The two policies should be statistically
indistinguishable. \textsc{premium} swaps the model to gpt-4.1.
\textsc{parallel} keeps gpt-4o-mini and replaces the system prompt
with a terse-clinical variant that is shorter and less hedged.
\textsc{unhelpful} keeps gpt-4o-mini and replaces the system prompt
with an off-topic instruction. It is the adversarial probe of the
safety claim. Sampling temperature is $0.7$ and maximum response length
is $800$ tokens for all five policies.

\paragraph{Judges and budget.}
The cheap judge is gpt-4o-mini and the oracle judge is gpt-4.1. The
cheap judge scores every $(\X, \A)$ pair on the panel ($500$ rows per
policy, $2{,}500$ in total). We then draw a uniform $25\%$ oracle slice.
For non-logger targets the audit slice has $n_{\mathrm{audit}} = 132$
rows; for the \textsc{base} self-audit holdout the calibrator-vs-audit
split is $80/20$ to break the calibration-vs-audit tautology, leaving
$n_{\mathrm{audit}} = 26$ (\cref{app:audit-holdout}). On the full panel
we additionally retain oracle labels on every row. These are used only
as ground truth for evaluating the estimator. None of the inference
uses the held-out labels. We treat $\alpha = 0.10$ as the headline tail
level and $\alpha = 0.20$ as a robustness check, with $B = 2{,}000$
cluster bootstrap replicates over prompts.

\paragraph{On a small panel and a small tail.}
At $n_0 = 500$ and $\alpha = 0.10$, the lower-tail population
corresponds to $50$ oracle rows. CVaR-CJE exists \emph{because} small
budgets make tail estimation otherwise infeasible. The cheap judge
scores all $500$ rows. The calibrator is anchored on the $132$ oracle
labels in the audit slice. Together they extract useful tail signal at
a sample size where pure-oracle CVaR estimation is visibly noisy. The
headline figure (\cref{fig:mvp}) and the cost-equivalence analysis
(\cref{sec:results-cost}) make this concrete.
