\section{Limitations}
\label{sec:limitations}

\paragraph{Oracle alignment (scope).}
We assume the operational oracle $Y$ aligns with stakeholder values; oracle selection itself is a governance question outside the scope of this work (Assumption~A0 in App.~\ref{app:assumptions-ledger}).

\paragraph{Overlap (positivity).}
IPS requires support overlap between $\pi_0$ and each $\pi'$; DR benefits from overlap but remains consistent via its outcome model when overlap is poor; Direct requires no overlap (it generates fresh responses under $\pi'$).
When overlap is poor, raw ratios are heavy-tailed and uncertainty inflates.
\emph{Mitigations:} Weight stabilization reduces dispersion and raises $\ESS$; if tails persist we (i) gate on $\ESS$ and Hill indices, (ii) use overlap weighting or cohort restriction, and (iii) run an online check when $\widehat{\alpha}_{\text{Hill}}{<}1$ or single–row dominance persists (App.~\ref{app:diagnostics}).

\paragraph{Judge assumptions (surrogate validity).}
Our calibration model uses a monotone single-index restriction (J2-M/J2-SI) as a stability/regularization choice. Correctness of level claims across policies is governed by \emph{mean transport} ($\E_{\pi'}[Y - f(S,X)] = 0$), which we audit; when the audit fails or evidence is weak, we widen/refresh the oracle slice or refuse level claims.
\emph{Mitigations:} (i) \textbf{With audit}: run the mean transport test per policy (\cref{prop:mean-transport}); fail $\to$ recalibrate or refuse levels. (ii) \textbf{Without audit}: surface reliability curves as indirect evidence; when evidence is weak, target labels where error concentrates.

\paragraph{Calibration failure modes.}
Reward calibration can fail in three distinct ways, each with observable signatures:
\begin{enumerate}[leftmargin=*,nosep]
\item \textbf{Policy-specific calibration:} The $S \to Y$ mapping differs across policies.
\emph{Signature:} Within-policy rankings accurate, cross-policy comparisons fail.
\emph{Test:} Policy-wise mean transport test (\cref{prop:mean-transport}). If $\E_{\pi'}[Y - f(S,X)] \neq 0$, surrogate values are biased for that policy.
\item \textbf{Extrapolation beyond range:} Target policy produces $S$ values outside the calibration range.
\emph{Signature:} Boundary flatness; \texttt{OutOfRange} $> 5\%$.
\emph{Test:} Coverage diagnostic (App.~\ref{app:diagnostics}).
\item \textbf{Temporal drift:} The $S \to Y$ mapping changes over time.
\emph{Signature:} Recent residuals larger than historical; calibration accuracy degrades.
\emph{Test:} Periodic mean transport test on fresh oracle batches.
\end{enumerate}

\paragraph{Scope of the mean transport test.}
The policy-wise mean transport test (\cref{prop:mean-transport}) is a \emph{necessary but not sufficient} condition for full surrogate transportability (S2): it guarantees that the surrogate is unbiased for policy-wise mean values, but does not rule out conditional miscalibration within subgroups or at the tails of the score distribution.
\emph{Mitigations:} perform subgroup-specific transport tests when fairness concerns apply; monitor reliability diagrams for regional deviations; use richer moment conditions for stronger tests (see remark after \cref{prop:mean-transport}).

\paragraph{Calibration coverage (identification).}
If a $\pi'$ pushes $S$ outside the labeled range, isotonic calibration flattens at the boundary and levels are not point–identified.
\emph{Mitigations:} flag \textsc{Limited Calibration Support} and set \RefuseLevel\ (report rankings and partial–ID bounds) until targeted labels cover the uncovered $S$ region (App.~\ref{app:diagnostics}).

\paragraph{Approximate sufficiency (bias modulus).}
When $\E[Y\mid X,A,S]\neq \mu(S)$, the residual $\Delta(X,A,S)$ induces bias proportional to calibration error.
\emph{Mitigations:} by Cauchy–Schwarz, $|\mathrm{Bias}|\le \|m-W_{\pi'}\|_2\,\|\Delta\|_2$; weight stabilization shrinks $\|m-W_{\pi'}\|_2$, so bias is second order when either calibration is tight or the violation small; we surface this via diagnostics and invoke \RefuseLevel\ when unbounded.

\paragraph{Temporal dependence and logger drift.}
Non–stationarity (launches, safety updates) can bias or widen intervals.
\emph{Mitigations:} report dependence–robust SEs (block/stationary bootstrap), shorten analysis windows, and monitor judge drift via rank–based/residual change detection with FDR control.

\paragraph{Oracle independence and leakage.}
Calibration-aware inference assumes the oracle slice is i.i.d.\ with non-overlapping folds.
\emph{Mitigations:} reuse deterministic folds across modules, de–duplicate the slice, and periodically refresh it.

\paragraph{Selection and multiplicity.}
Scanning many $\pi'$ inflates winner's curse.
\emph{Mitigations:} use FDR control (BH/BY), optionally an outer split for influence-function stacking to reduce selection optimism, and emphasize pre–specified contrasts.

\paragraph{Teacher forcing and API drift.}
Accurate propensities require deterministic, chat–native TF (stable tokenizer/template) with additivity/conditionality invariants; missing/invalid TF corrupts ratios.
In our experiments, 39 of 5,000 prompts (0.8\%) were filtered: 11 due to base-policy TF conformance failures, and 28 due to missing target-policy logprobs. While small, we report this explicitly: practitioners should expect some data loss from TF gaps, and filtering should always be logged for reproducibility. This also highlights the current state of TF support from LLM providers: major closed-source providers (OpenAI, Anthropic, Google) do not currently support teacher forcing for chat models, and among open-weight hosting providers, Fireworks AI was the only service we found with reliable TF support.
Even for our TF reliability test (clone = base with different seed), raw ESS is 26\% rather than the theoretical 100\%, reflecting API-level non-determinism and floating-point divergence in log-probability summation; weight stabilization restores this to 99\% (\cref{tab:weight-diagnostics}). This 26\% is substantially higher than other policies (0.4--0.7\%), confirming TF captures real distributional similarity, but it is far from the theoretical 100\% and suggests propensity estimates carry meaningful error even before overlap considerations.
OPE failure in our experiments reflects two compounding issues: (i) TF brittleness corrupts propensity estimates, and (ii) CLE limits precision even with perfect propensities. We cannot cleanly separate their contributions, but both matter: if TF were the only problem, weight stabilization should improve ranking more than it does; if CLE were the only problem, clone should have ESS $\approx$ 100\%.
\emph{Mitigations:} enforce schema/conformance checks, ledger failures, and treat results as conditional on TF quality (App.~\ref{app:impl}).

\paragraph{Subgroups and fairness.}
Calibration quality and ESS gains may differ across subgroups.
\emph{Mitigations:} provide subgroup diagnostics (ESS, reliability) and, when feasible, use subgroup–specific calibration/weights or constrained pooling.

\paragraph{Judge informativeness (garbling).}
Coarser judges raise the surrogate information bound and widen CIs.
\emph{Mitigations:} prefer richer rubrics (multi–dimensional $S$ with stable aggregation) and validate with coarsening ablations (empirical Blackwell monotonicity).

\paragraph{Compute.}
Calibrated DR adds one rollout\,+\,judge per $(X,\pi')$; reward calibration refits for calibration-aware inference add modest overhead.
We amortize via TF caches, shared folds, and a small stacking library.

\noindent\textbf{Ethics Statement.}
We analyze retrospective logs that may include sensitive content.
Diagnostics/gates prevent overconfident claims under poor overlap/coverage and surface judge drift.
When identification fails, we report rankings only (\RefuseLevel) and recommend targeted labeling or online checks.
Any deployment should assess subgroup reliability and adopt privacy safeguards for logs.

\noindent\textbf{Reproducibility Statement.}
Exact prompts, schema, TF contract, pseudocode, and numerics appear in the appendices.
Code and data are available at \url{https://github.com/cimo-labs/cje-arena-experiments}; the CJE library is available via \texttt{pip install cje-eval} (\url{https://github.com/cimo-labs/cje}).
