\section{Monte Carlo and Estimation Plan}
\label{app:mc}

The simulation appendix is secondary to the theory appendix. Its role is to
stress-test the audit-gated estimator under controlled laws where the target
estimand, the transport null, and the expected rejection behavior are known in
advance.

\subsection{Simulation Design Grid}

Each design reports the mean value $V(\ptarget)$, the lower-tail value
$\CVaR_\alpha(\ptarget)$, whether mean transport holds, whether shortfall
transport holds near the lower-tail optimizer, and which audit moment should
move under the alternative.

\begin{table}[htbp]
\centering
\small
\resizebox{\linewidth}{!}{%
\begin{tabular}{llll}
\toprule
Design & Estimand contrast & Audit-null status & Expected behavior \\
\midrule
Null shortfall transport
& mean and lower-tail level
& both moments valid
& rejection near nominal \\
Mean transport only
& equal mean, shifted lower tail
& $g_2$ invalid
& mean audit passes; CVaR audit rejects \\
Threshold perturbation
& correct shortfall map, wrong tail mass
& $g_1$ invalid
& threshold moment drives rejection \\
Shortfall bias
& correct tail mass, biased shortfall map
& $g_2$ invalid
& shortfall moment drives rejection \\
Discrete rating outcome
& atom at the optimizer
& tie rule required
& naive indicator moment can over-reject \\
Similar means, different tails
& same $V(\ptarget)$, different $\CVaR_\alpha(\ptarget)$
& design-specific
& tail ranking separates policies before mean ranking does \\
Oracle-budget sweep
& finite-label precision
& design-specific
& uncertainty and refusal rate improve with oracle budget \\
\bottomrule
\end{tabular}
}
\caption{Simulation scenarios for the online appendix.}
\label{tab:mc-plan}
\end{table}

\subsection{Estimands and Null Status}

For each design, the appendix should state:
\begin{itemize}[leftmargin=*,nosep]
\item the policy law and oracle-outcome law;
\item the oracle mean $V(\ptarget)$ and lower-tail value
$\CVaR_\alpha(\ptarget)$;
\item the reference surrogate $f(\Sscore,\X)$ and shortfall surrogate
$h_t(\Sscore,\X)$;
\item whether $\E_\ptarget[\Y-f(\Sscore,\X)]=0$;
\item whether $\E_\ptarget[\shortfall{t}{\Y}-h_t(\Sscore,\X)]=0$ near the
population optimizer;
\item which audit moments should be zero and which should move.
\end{itemize}

\subsection{Reported Metrics}

Report metrics separately for audit-accepted and audit-rejected runs:
\begin{itemize}[leftmargin=*,nosep]
\item audit size under the null and audit power under each alternative;
\item estimator bias and RMSE conditional on audit acceptance;
\item confidence-interval coverage conditional on audit acceptance;
\item probability of \RefuseLevel{};
\item pairwise lower-tail ranking accuracy among audit-accepted policies;
\item sensitivity to $\alpha$, oracle fraction, calibration size, grid
resolution, and tail density.
\end{itemize}

\subsection{Result Tables to Fill}

The online appendix should reserve one table per design family:
\begin{enumerate}[leftmargin=*,nosep]
\item a size table for the null shortfall-transport design;
\item a power table separating $g_1$ alternatives from $g_2$ alternatives;
\item a discrete-outcome table comparing the interval and randomized tie rules;
\item a lower-tail ranking table for policies with similar means;
\item an oracle-budget table showing bias, RMSE, coverage, interval length, and
\RefuseLevel{} rate.
\end{enumerate}

The main text should only import the minimal subset needed to support the
empirical claim. The online appendix should keep the full design grid so that
readers can distinguish estimator error from deliberate audit refusal.
