\section{Dataset Survey and the Arena-Tail Construction}
\label{app:dataset}

This appendix documents the empirical dataset survey that motivates the
Arena-Tail mixture and reports preliminary CVaR-bite findings on
public datasets where in-data multi-policy structure permits estimation
without fresh policy generation. The full survey log is in
\texttt{cvar\_v4/scoping.md}; per-dataset 20-block diagnostics are in
\texttt{cvar\_v4/scoping\_data.md}.

\subsection{Ten-Dataset Survey: What Already Exists}
\label{app:dataset:survey}

We surveyed 10 public datasets along six dimensions: prompt
distribution match to the original CJE Arena setting (P), in-data
multi-policy structure (\(\Pi\)), shipped cheap-S/oracle-Y stack (S/Y),
empirical CVaR-bite vs.\ mean (C), built-in audit covariate
discriminativeness (A), and domain demand for worst-case evaluation
(D). Each dimension is graded 1--5, with 5 indicating ``best fit for
CVaR-CJE replication of the original pipeline.'' Total scores out of
30:

\begin{table}[h]
\centering
\footnotesize
\begin{tabular}{rlcp{3.4cm}rrrrrrr}
\toprule
\# & Dataset & Year & Domain / topic & P & \(\Pi\) & S/Y & C & A & D & Total \\
\midrule
1 & UltraFeedback & 2023 & Instruction-following quality (multi-dim) & 5 & 5 & 5 & 5 & 3 & 2 & 25 \\
2 & HH red-team-attempts & 2022 & Adversarial harmlessness (red-team transcripts) & 3 & 5 & 4 & 5 & 4 & 4 & 25 \\
3 & HealthBench & 2025 & Medical / clinical advice & 4 & 1 & 4 & 4 & 5 & 5 & 23 \\
4 & RealToxicityPrompts & 2020 & Toxicity / content moderation & 3 & 1 & 5 & 4 & 5 & 4 & 22 \\
5 & WildJailbreak & 2024 & Synthetic adversarial safety (4-quadrant) & 4 & 1 & 4 & 4 & 5 & 4 & 21 \\
6 & WildChat-4.8M (shuffled) & 2024/25 & Naturalistic ChatGPT/o1-style real chat & 5 & 3 & 4 & 3 & 2 & 3 & 21 \\
7 & Arena-140k (anchor) & 2024 & General chat preference (Chatbot Arena) & 5 & 5 & 2 & --- & 3 & 2 & 21 \\
8 & HarmBench + StrongREJECT & 2024 & Jailbreak / adversarial attack research & 2 & 1 & 4 & --- & 2 & 4 & 16 \\
9 & BeaverTails & 2023 & Safety-tagged QA (14 harm classes) & 3 & 1 & 2 & 1 & 3 & 4 & 15 \\
10 & PKU-SafeRLHF & 2024 & Safety preference pairs (19 harm classes) & 3 & 3 & 2 & 1 & 2 & 4 & 15 \\
\bottomrule
\end{tabular}
\caption{Dataset survey scores. ``Year'' is the year of the canonical
public release (arXiv-paper year). ``Domain / topic'' is the descriptive
label of what the dataset is about; ``D'' is the 1--5 rating of how
much that domain demands worst-case (CVaR) evaluation. Top tier
(\(\geq\)23) are direct CVaR-CJE replication candidates. Mid tier
(21--22) are domain-relevant complements. Bottom tier (\(\leq\)16) are
prompt-source seeds for Arena-Tail rather than standalone targets.}
\label{tab:dataset-survey}
\end{table}

\subsection{Preliminary In-Data Findings}
\label{app:dataset:findings}

Five datasets ship enough multi-policy structure and continuous-enough
\(Y\) to permit cross-policy CVaR comparisons without fresh policy
generation. We report these as preliminary evidence that the
same-mean--different-tail pattern is a real phenomenon in public LLM
evaluation data, not an artifact of any particular benchmark.

\paragraph{HH red-team-attempts (n=38{,}961).} Anthropic's red-team
transcripts ship 12 in-data cells (\(\{\)plain LM, context distillation,
rejection sampling, RLHF\(\} \times \{2.7\)B\(, 13\)B\(, 52\)B\(\}\))
with a continuous preference-model score
(\texttt{min\_harmlessness\_score\_transcript}). The pair
\((\texttt{rlhf}\,|\,\)13B\(, \texttt{rejection sampling}\,|\,\)2.7B\()\)
has 95\% bootstrap mean CIs that overlap heavily
(\([+1.40, +1.46]\) vs.\ \([+1.45, +1.54]\)) but 95\% bootstrap
\(\CVaR_{0.05}\) CIs that are disjoint
(\([-0.30, -0.06]\) vs.\ \([-1.40, -0.84]\)). The CVaR gap is
\(14.6\times\) larger than the mean gap. Mean evaluation correctly
calls the policies indistinguishable; CVaR cleanly resolves a 0.97-unit
harmlessness ranking.

\paragraph{UltraFeedback (n=255{,}612).} 17 in-data models scored on a
\([1, 10]\) GPT-4-Turbo aggregate. Within the \texttt{ultrachat}
prompt-source slice, \texttt{llama-2-70b-chat} and \texttt{mpt-30b-chat}
have means 4 thousandths apart on a 1--10 scale (statistically
indistinguishable at any reasonable \(n\)) but \(\CVaR_{0.05}\)
1.4 points apart, a \(140.5\times\) ratio. 39 within-source same-mean
\(\times\) different-tail pairs total. The pattern is robust to prompt
stratification.

\paragraph{WildChat-4.8M (n=99{,}081 shuffled stream).} 5 in-data
models including \texttt{o1-mini-2024-09-12}, \texttt{gpt-4o},
\texttt{gpt-4o-mini}, \texttt{gpt-4-0314}, \texttt{gpt-3.5-turbo-0301},
scored by per-turn Detoxify max. \texttt{o1-mini} vs.\ \texttt{gpt-4o}
have \(\Delta\)mean = 0.0003 (statistically tied) and
\(\Delta\CVaR_{0.05}\) = 0.008, a \(32\times\) ratio. Reasoning-trained
models pay a measurable CVaR dividend that mean evaluation misses.

\paragraph{HealthBench (n=14{,}592 (prompt, completion) cells in
\texttt{oss\_meta\_eval}).} Aggregating physician binary labels into
rubric-percent \(Y\) gives \(\CVaR_{0.05}\) ranging from 0.000 (on
emergency\_referrals, health\_data, context\_seeking, global\_health
themes) to 0.500 (on hedging, communication, complex\_responses
themes). Per-theme \(q_{0.05}\) spread of 0.50 is the largest
within-dataset audit-discriminative heterogeneity in the survey.

\paragraph{RealToxicityPrompts (n=98{,}892).} The dataset's
\texttt{challenging} boolean (1.2\% of corpus) holds 7.8\% of the
worst-1\% Y\_safe (= \(1 - \text{toxicity}\)) tail mass: a
\(6.5\times\) concentration. Conditional \(q_{0.05}\) is 0.035 (under
\texttt{challenging=True}) vs.\ 0.084 otherwise. A single boolean flag
the audit must fire on for any policy that does not handle benign and
challenging prompts differently.

\subsection{The Cheap-S Admissibility Condition}
\label{app:dataset:cheap-s}

A coverage-and-cheap-S sweep on the HH red-team headline pair surfaces
a structural admissibility condition that the original CJE paper does
not need to make explicit but that CVaR-CJE does. With logger
\(\pi_0 = \texttt{rlhf}\,|\,\)52B and two cheap-\(S\) choices:

\begin{itemize}[leftmargin=*,nosep]
\item \(S = -\log(\text{transcript chars} / 1000)\) (length-based,
response-side but Y-misaligned): per-policy \(\rho(S, Y)\) varies
from \(+0.14\) to \(+0.62\) across the 12 cells. The Direct
\(\CVaR_{0.05}\) estimate \emph{has the sign flipped} relative to
truth on the headline pair, with absolute errors of 0.75--1.40.
Errors do not shrink with oracle coverage.
\item \(S = \texttt{task\_descripton\_harmlessness\_score}\) (Y-aligned
but prompt-side): \(|\rho(S, Y)|\) collapses to under 0.30 because
the score is a function of the prompt only and cannot distinguish
responses generated by different models on the same prompt. The
Direct estimate is uniform across within-family targets, yielding
degenerate \(\Delta \approx 0\).
\end{itemize}

A cheap \(S\) admissible for level claims must be \emph{both}
response-side \emph{and} Y-aligned with consistent sign across
policies. Length is the former but not the latter; task-description
score is the latter but not the former. The audit reliably catches
out-of-family transport failures (audit fires on context-distillation
and plain-lm targets in our HH demo regardless of \(S\) choice) but
does not protect against bias that is symmetric across all
within-family targets. This is a structural property of the framework,
not a bug.

\subsection{Audit Asymmetry in Logger Choice}
\label{app:dataset:asymmetry}

End-to-end Direct CVaR-CJE plus Wald two-moment audit on HH red-team
with two logger choices yields a striking asymmetry. With logger
\(\pi_0 = \texttt{rlhf}\,|\,\)52B (highest mean \(Y\)), the audit fires
on 5 of 8 out-of-family targets and correctly accepts 3 of 8
within-family targets, with Direct \(\CVaR_{0.05}\) errors of 0.3--1.3
within-family. With logger \(\pi_0 = \texttt{context distillation}\,|
\,\)52B (worst mean \(Y\) of the 12 cells), the audit accepts on
\emph{all 9} cells \emph{including those with Direct
\(\CVaR_{0.05}\) errors of 4--5 units}.

The mechanism is the structure of the quantile-coverage moment.
When the logger has the worst tail in the panel, \(\hat t\) is
pinned to the logger's empirical 5\%-quantile (around \(-3.6\) to
\(-4.7\)). For target cells whose \(Y\) is mostly positive, almost
no observations fall below \(\hat t\); the moment
\(g_1 = \mathbf{1}\{Y \le \hat t\} - \alpha\) collapses to roughly
\(0 - 0.05\), and the calibrator-shortfall moment
\(g_2 = (\hat t - Y)_+ - \hat f(S)\) compares two near-zeros. The
audit's bootstrap variance estimate inflates because \(\hat t_b\)
varies across reps when the optimizer cannot find a good fit, making
the test statistic small.

\paragraph{Operational rule.} Pick a logger whose \(Y\) distribution
dominates (higher \(Y\) = safer) the targets one wants to certify.
The audit refuses to certify targets that are \emph{worse} than the
calibrator predicts (the operationally important case) but does not
fire on targets that are \emph{better} than predicted. The asymmetry
is by design: the audit is an alarm for misleading level claims, not
a symmetric goodness-of-fit test.

\subsection{Arena-Tail Construction Implications}
\label{app:dataset:construction}

The dataset survey supports the Arena-Tail construction in
\cref{sec:arena-tail} as follows.

\begin{itemize}[leftmargin=*,nosep]
\item \emph{Backbone (50\%).} Arena-140k (135K user-conversation
prompts) is the natural prompt-distribution match for the original
CJE Arena setting at \(27\times\) the prompts. Pairwise winner labels
are incompatible with per-policy \(\CVaR_\alpha\) as a scalar, so the
dataset is used as a prompt source rather than a standalone target.

\item \emph{Adversarial stratum (20\%).} HarmBench + StrongREJECT
(combined 713 prompts) and WildJailbreak's
\texttt{adversarial\_harmful} quadrant (82,728 prompts) provide
prompts where the worst-case response is the deployment-determining
behavior. WildJailbreak's four-quadrant
\texttt{data\_type} partition lets us test two orthogonal
audit-failure axes simultaneously: a \(\pi_{\text{safety}}\) policy
that over-refuses fails on the
\texttt{adversarial\_benign} quadrant; a \(\pi_{\text{adversarial}}\)
policy that under-refuses fails on the
\texttt{adversarial\_harmful} quadrant.

\item \emph{Safety-sensitive stratum (15\%).} BeaverTails (14 harm
classes) and PKU-SafeRLHF (19 harm classes, severity-graded) provide
fine-grained harm-class stratification. Both have discrete or binary
in-data \(Y\), so they enter the mixture as \emph{prompt sources}
only; \(Y\) is elicited freshly under our chosen oracle.

\item \emph{Domain stratum (10\%).} HealthBench (6,000 multi-turn
clinical conversations across 7 themes) provides the highest-domain-
demand subset (life-safety stakes) and the strongest pre-built
audit-discriminative covariate (per-theme \(q_{0.05}\) spread of
0.50). The medical-emergency-referral theme is the canonical case
where mean evaluation provably misses what worst-case evaluation
catches (see OpenAI HealthBench paper's worst-at-\(k\) finding for
\texttt{o3}, where worst-at-16 score is roughly one-third of mean).

\item \emph{Naturalistic stratum (5\%).} WildChat-4.8M shuffled
stream provides real-world ChatGPT-style conversations including
1.5M flagged-toxic. The non-toxic shard reaches 5 in-data models
(\(\{\)gpt-3.5-turbo, gpt-4, gpt-4o, gpt-4o-mini, o1-mini\(\}\));
the toxic shard requires explicit \texttt{data\_files} access.
\end{itemize}

The total budget for Arena-Tail (100K prompts \(\times\) 5 policies
\(\times\) \(\sim\)400 output tokens, plus a 15\% oracle slice on
\(\sim\)75K calls) is approximately \$7,800 at 2026-Q2 inference rates,
of which \$2,500 is closed-frontier policy generation and \$5,250 is
oracle annotation; open-weight policies contribute under \$50 in
generation. This is roughly \(140\times\) the cost of the original CJE
paper's pilot but yields a stratified pool whose
audit-discriminative covariate (the prompt stratum) is built into the
construction rather than relying on a single deliberately-bad policy.
